---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

# Use 'badger' to place badges
library(badger)
```


```{r, include = FALSE}
# Data sources
ERA5 <- data.frame(Dataset = "ERA5-Land Hourly",
                   Source = "ECMWF",
                   Link = "<a href = 'https://cds.climate.copernicus.eu/cdsapp#!/dataset/10.24381/cds.e2161bac?tab=overview' target='_blank' rel='noopener noreferrer'>ERA5-Land</a>",
                   Citation = "DOI: <a href = 'https://doi.org/10.24381/cds.e2161bac' target='_blank' rel='noopener noreferrer'>10.24381/cds.e2161bac</a>")

SNODAS <- data.frame(Dataset = "SNODAS",
                     Source = "NOAA",
                     Link = "<a href = 'https://nsidc.org/data/g02158' target='_blank' rel='noopener noreferrer'>NSIDC</a>",
                     Citation = "DOI: <a href = 'https://doi.org/10.7265/N5TB14TC' target='_blank' rel='noopener noreferrer'>10.7265/N5TB14TC</a>")

Daymet <- data.frame(Dataset = "Daymet v4",
                     Source = "NASA",
                     Link = "<a href = 'https://daac.ornl.gov/DAYMET/guides/Daymet_Daily_V4.html' target='_blank' rel='noopener noreferrer'>ORNL DAAC</a>",
                     Citation = "<a href = 'https://daymet.ornl.gov/files/Thornton_Daymet_V4_submitted_2021-01-20.pdf' target='_blank' rel='noopener noreferrer'>Thornton et al. 2020</a>")

# Combine
data_sources <- rbind(ERA5, SNODAS, Daymet)

# Sort
data_sources <- data_sources[order(data_sources$Dataset), ]
```
# snowdl

<!-- badges: start -->
`r badge_license("GPL-3")`
`r badge_custom("repo status", "WIP", "yellow", "https://www.repostatus.org/#wip")`
`r badge_devel("bsmity13/snowdl", "blue")`
<!-- badges: end -->

The goal of `snowdl` is to make it easy to download snow data (*e.g.*, snow depth, snow density, snow-water equivalent) from various sources (*e.g.*, SNODAS, Daymet).

## Installation

Install the development version from [GitHub](https://github.com/bsmity13/snowdl) with:

``` r
# install.packages("devtools")
devtools::install_github("bsmity13/snowdl")
```
This package is not yet operational. Check back soon for progress!

## Available data sources

*Sorted alphabetically by dataset name*

`r knitr::kable(data_sources, row.names = FALSE, escape = TRUE)`

## Important Notes

  *   Daymet is probably not a great source for SWE. Based on my reading, they treat it more like a nuisance parameter than a quanity of interest. See this link for their [Snow Water Equivalent Clarification](https://daac.ornl.gov/DAYMET/guides/Daymet_V3_CFMosaics.html#qualityassess). Note, this clarification was made in reference to V3, but still applies based on newest literature for V4.
  
  *   Further, Daymet has (apparently) different units for SWE than other sources (but not really). Daymet uses kg/m^2, while other sources use m (depth if snow was melted). To convert `snowdl` will offer the option to multiply by area of the pixel (kg/m^2 * m^2/1 = kg) to get mass of water, convert to cubic meters (1 kg = 1 L H2O = 0.001 m^3), and then get depth by dividing by area (m^3/1 * 1/m^2 = m). Perhaps more useful to have units in mm, so again multiply by 0.001 m = 1 mm.
    -   Note Daymet comes with lcc projection and units = m. Resolution is 1000 x 1000, so area is 1e6 m^2.
    -   Therefore, conversion becomes `x * 1e6 * 0.001 * 0.001`. All conversions cancel and resulting units are mm.
    -   To be clear, km/m^2 = mm in this case.
